Irt plot extra

### 2022-03-24 manuscript.Rmd
Reference file for the packages is separated from literature references

bibliography      : ["references.bib"]

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#reversecoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(tabledown)
library(readxl)
library(koRpus)# stable release
library(koRpus.lang.en)
library(reshape)
library(ggsci)
library(ggtext)
r_refs("references.bib")
```

@@

---
nocite: |
  `r cite_r("references.bib")`
  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
  [@horne1976self][@roenneberg2003life][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita][@grandner2014development]
---

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long form (23-item) and short form (18-item) of LEBA. ', out.height='100%', out.width='100%'}
knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
```

@@

```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
knitr::include_graphics('Figures/Figure2.png')

@@

```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
knitr::include_graphics('Figures/Figure3.png')

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)` [@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].  Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for conducting the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |.30|. The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:fig:efa-plot A) depicts the correlation matrix.

@@

Scree plot ( Figure \@ref(fig:efa-plot) B) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 2**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis'}

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (**Supplementary Table 3**). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**)).

@@

```{r saveWrightmao, include=FALSE, warning=F, message=F}
#This chunk holds codes for saving the wright-map
jpeg("Figures/wm.png", width = 800, height = 750)
WrightMap::wrightMap(estimation, threshold, 
          item.prop = 0.65,

>>>>

bibliography      : ["references.bib", "lib_references.bib"]

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#reversecoding 
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(ggcorrplot)
library(semTable)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(tabledown)
library(readxl)
library(koRpus)# stable release
library(koRpus.lang.en)
library(reshape)
library(ggsci)
library(ggtext)
r_refs("lib_references.bib")
```

@@

---
nocite: |
  `r cite_r("lib_references.bib")`
  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
  [@horne1976self][@roenneberg2003life][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita][@grandner2014development]
---

@@

```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='100%', out.width='100%'}
knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
```

@@

```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure2.png')

@@

```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern', out.height='100%', out.width='250%'}
knitr::include_graphics('Figures/Figure3.png')

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)` [@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].  Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for conducting the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |.30|. The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`. Figure \@ref(fig:efa-plot-print A) depicts the correlation matrix.

@@

Scree plot ( Figure \@ref(fig:efa-plot-print) B) suggested a six-factor solution. However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 2**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

@@

```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis', out.height='100%', out.width='110%'}

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (**Supplementary Table 3**). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**).

@@

```{r saveWrightmao, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#This chunk holds codes for saving the wright-map
jpeg("Figures/wm.png", width = 800, height = 750)
WrightMap::wrightMap(estimation, threshold, 
          item.prop = 0.65,
